---
title: "human naïve pluripotent stem cells"
output: html_document
date: "2024-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Run SCSES step by step (smart-seq2 data)

#### Step1. Read configure file

```{r}
library(SCSES)
#paras_file: path to configure file generated in the previous step
paras_file = "/disk/lvxuan/Single-Splicing/src/package/SCSES/analysis/nPSC.json"
paras = readSCSESconfig(paras_file)
```

#### Step2. Get gene expression

##### TPM matrix

```{r}
featurecounts.path = getGeneExpression(paras) 
rds.path = getEXPmatrix(paras)
```

#### Step3. Detect splicing events

```{r}
pseudobulk.path = createPseudobulk(paras)
#if you meet:
#irfinder: error while loading shared libraries: libboost_iostreams.so.1.71.0: cannot open shared object file: No such file or directory
old.ld=Sys.getenv("LD_LIBRARY_PATH")
Sys.setenv(LD_LIBRARY_PATH = paste0("/disk/lvxuan/lib:", old.ld))
event.path = detectEvents(paras)
```

#### Step4. Quantify splicing events

```{r}
rawrc.path = getRawRC(paras)
rawpsi.path = getRawPSI(paras)
rawrds.path = mergeSplicingValue(paras)
processed.data.path = preprocessEvent(paras)
```

#### Step5. Constructs similarity networks

```{r}
cellnet.path = getCellSimilarity(paras)
eventnet.path = getEventSimilarity(paras)
```

#### Step6. Imputation

``` {r}
Imputed.data.path = ImputationAll(paras)
```

A list of three imputation strategies result will be saved to `work_path/imputation/`.

#### Step7. Estimation

``` r
#rds_imputed_file: path to the list of three imputation strategies results generated in the previous step
Imputed.data.path = Estimation(paras,rds_imputed_file)
```

##### Fine-tune the model

``` r
ftrc.path = getFtRawRC(paras)
ftpsi.path = getFtRawPSI(paras)
ftrds.path = mergeFtSplicingValue(paras)
ftmodel.path = FtClassifier(paras)
#rds_imputed_file: path to the list of three imputation strategies results generated in the previous step
Imputed.data.path = Estimation(paras,rds_imputed_file)
```

A list of final imputation of PSI values will be saved to `work_path/imputation/`.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
